Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-04-19 meta_analysis_sexual_selection_pop_fitness.Rmd
19/4 update

```{r warning=FALSE, message=FALSE, results='hide'}
library(knitr)
library(pander)
library(compute.es)
library(metafor)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
source("Vdodge_function.R") # nice function for ggplot
```

@@

### Data extraction

@@

>Justin Says: I think I need to clean up some of the notes and make them more readable

@@

**mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance). Rows without these values had hedges g' derived from summary statistics (F, z, chi-square etc.).

@@

> Although I am not sure whether having the raw values would be better. In addition whether it is worth it to add in summary polygons (effect sizes) for a grouped outcome

> Luke says: if you are plotting RESIDUAL effect sizes, doesn't that mean this plots shows each effect size, relative to the grand mean effect size? Like, -0.05 means it is below average, but the effect is still positive since the grand mean is +0.1. This is probably not what we want.

> I have modified the code below so that it plots the resid + the grand mean. But I think since model is intercept only, this might be the same thing as the raw data... not sure. Have a think, or just plot all the raw effect sizes +/- their 95% CIs, instead of the residuals.

> Also try to make it clear what positive g means (I guess positive g means higher fitness when SS is present/strong?)

```{r, fig.height=25, fig.width=10}
# Run standard random effects model
# forest.model <- rma.mv(g, var.g, 
#                        mods = ~ 1 + Sex * Environment + Taxon,
#                        random = list(~ 1 | Study.ID, 
#                                        ~ 1 | Outcome),
#                        method = "REML", 
#                        data = prelim.data)
# 
# # Obtain residuals
# resstandards <- (rstandard.rma.mv(forest.model, 
#                                    type="response"))
# 
# # Obtain grand mean effect size    <- ADDED BY LUKE
# grand.mean <- as.numeric(forest.model$b)
# 
# # Create new df with residuals replacing raw
# df.forest.model <- prelim.data                     # <- Luke says: you could just use prelim.data itself, not the residuals?
# df.forest.model$g <- resstandards$resid + grand.mean   # <- ADDED BY LUKE
# df.forest.model$sei <- resstandards$se

@@

# define upper and lower bounds
prelim.data$lowerci <- prelim.data$g - 1.96*(sqrt(prelim.data$var.g))
prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))

# Get author and year in one
short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
                                 short = prelim.data$Authors %>% unique() %>% 
  as.character() %>% 
  strsplit(split = ",") %>% 
  sapply(FUN=function(x) x[1])) %>%
  left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
  mutate(suffix = "")

# Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
dups <- with(short.author.names, table(short, Year)) %>% melt()
dups <- dups[dups$value > 1, ]
for(i in 1:nrow(dups)){
  short.author.names$suffix[
    short.author.names$short == dups$short[i] &
      short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
}

# Add the AuthorYear column to the dataframe of effect sizes
short.author.names <- short.author.names %>%
  mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
  select(long, AuthorYear)
prelim.data <- prelim.data %>% 
  left_join(short.author.names, by = c("Authors" = "long"))

#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%
  ggplot(aes(y=reorder(AuthorYear, -g), x = g, shape = Sex, color = Outcome.Class)) +
  geom_errorbarh(aes(xmin = lowerci, 
                     xmax = upperci), height = 0.1) +
  geom_point(size = 1.5) +
  scale_x_continuous(limits=c(-5, 5), name='Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +
  scale_color_discrete(name = "Relationship\nto fitness") + 
  ylab('Reference') + 
  geom_vline(xintercept=0, color='black', linetype='dashed')+
  facet_grid(Outcome_f~., scales= 'free', space='free')+
  theme(strip.text.y = element_text(angle = 0))
ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 25, width = 12)
p.meta
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes. Positive values indicate fitness benefits of sexual selection.

###Quantitative summary using bootstrapped means

We can obtain a bootstrap weighted mean for the entire dataset. Although this does not take into account any moderator variables it does provide a rough guide on where most of the datapoints sit:

```{r}
#Run function
get.CIs.for.weighted.mean <- function(x, weights){
  total.resamples <- 10000
  num.chunks <- ceiling(length(x)*total.resamples / 10^7) # To be nice to RAM, let's keep these to ten million or less 
  if(num.chunks == 1){
    rand <- sample(length(x), length(x)*total.resamples, replace = TRUE)
    resampled.weighted.means <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:total.resamples, each = length(x))) %>% 
      group_by(replicate) %>% 
      summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean
  }

  else{
    resampled.weighted.means <- vector(mode = "list", length = 0)
    number.of.resamples <- floor(total.resamples/num.chunks)
    final.chunk.size <- total.resamples - number.of.resamples * (num.chunks-1)
    for(i in 1:num.chunks){
      if(i == num.chunks) number.of.resamples <- final.chunk.size
      rand <- sample(length(x), length(x) * number.of.resamples, replace = TRUE)
      resampled.weighted.means[[i]] <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:number.of.resamples, each = length(x))) %>% 
        group_by(replicate) %>% 
        summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean
    }
    resampled.weighted.means <- unlist(resampled.weighted.means)
  }

  data.frame(w.mean = median(resampled.weighted.means),
             lowerCI = quantile(resampled.weighted.means, probs = 0.025) %>% as.numeric(),
             upperCI = quantile(resampled.weighted.means, probs = 0.975) %>% as.numeric())
}

#Get weights
prelim.data$Standard.weights <- (1/prelim.data$var.g)

#Run function with weights
get.CIs.for.weighted.mean(prelim.data$g, prelim.data$Standard.weights) %>% pander()
```

>Could this be used as a line in the forest plot showing the average (or as a polygon at the bottom), or done for each outcome?

@@

> Let's just run one big model then cull from there

@@

```{r}
model.preliminary <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + Generations + Blinding, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = prelim.data)

summary(model.preliminary)
```
<br></br>
**A note on random effects** Here we utilise crossed random effects of Study.ID and Outcome. Nesting Outcomes within Study.ID can also be achieved through ``random = ~ 1 | Study.ID/Outcome``. However given that the same outcome is expected to be measured in the same/very similar way between studies we used a crossed random effects design.

@@

```{r, warning=FALSE}
#Restrict the dataset for unambiguous outcomes and environments 
restricted.data <- prelim.data %>% 
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated") %>% 
  mutate(Sex = as.character(Sex), 
         Environment = as.character(Environment), 
         Outcome.Class.2 = as.character(Outcome.Class), 
         Enforced.Monogamy = as.character(Enforced.Monogamy))

@@

The result is a model with estimates for various taxa, species, sexes and environments. To make sense of these estimates we should obtain average predictions for each moderator variable class of interest. We can do that by using a modified version version of a function used by Holman 2017. Here it alows us to cluster predictions for the different moderators of interest: Sex, environment, taxon etc. This is done by obtaining predictions using the base ``predict()`` function for the ``rma.mv()`` objects that have been previously created
```{r}
# function that makes predict.rma work like a normal predict() function, instead of the idiosyncratic way that it works by default.
get.predictions.complete <- function(newdata){
  B<-0; F<-0; Stressed<-0; Cricket<-0; Fly<-0; Guppy<-0; Mite<-0; Mouse<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Unstressed<-1
  if(newdata[3] == "Cricket") Cricket<-1
  if(newdata[3] == "Fly") Fly<-1
  if(newdata[3] == "Guppy") Guppy<-1
  if(newdata[3] == "Mite") Mite<-1
  if(newdata[3] == "Mouse") Mouse<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1

>>>>

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(tidyr)
library(compute.es)
library(metafor)
library(plyr)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
source("Vdodge_function.R") # nice function for ggplot
```

@@

###Inclusion/Exclusion criteria

@@

@@

**mean/sd/n.low/high**: The means, standard deviation and sample size for the low or high sexual selection treatments, used to calculate lnCVR (meta-analysis of variance). Rows without these values (NA) had hedges g' derived from summary statistics (F, z, chi-square etc.).

@@

```{r, fig.height=18, fig.width=12}
# Run standard random effects model
# forest.model <- rma.mv(g, var.g, 
#                        mods = ~ 1 + Sex * Environment + Taxon,
#                        random = list(~ 1 | Study.ID, 
#                                        ~ 1 | Outcome),
#                        method = "REML", 
#                        data = prelim.data)
# 
# # Obtain residuals
# resstandards <- (rstandard.rma.mv(forest.model, 
#                                    type="response"))
# 
# # Obtain grand mean effect size    <- ADDED BY LUKE
# grand.mean <- as.numeric(forest.model$b)
# 
# # Create new df with residuals replacing raw
# df.forest.model <- prelim.data                     # <- Luke says: you could just use prelim.data itself, not the residuals?
# df.forest.model$g <- resstandards$resid + grand.mean   # <- ADDED BY LUKE
# df.forest.model$sei <- resstandards$se

@@

# define upper and lower bounds
prelim.data$lowerci <- prelim.data$g - 1.96*(sqrt(prelim.data$var.g))
prelim.data$upperci <- prelim.data$g + 1.96*(sqrt(prelim.data$var.g))
# 
# # Get author and year in one
# short.author.names <- data.frame(long = prelim.data$Authors %>% unique(),
#                                  short = prelim.data$Authors %>% unique() %>% 
#   as.character() %>% 
#   strsplit(split = ",") %>% 
#   sapply(FUN=function(x) x[1])) %>%
#   left_join(prelim.data %>% select(Authors, Year) %>% distinct(), by = c("long" = "Authors")) %>%
#   mutate(suffix = "")
# 
# # Sometimes there are multiple papers with the same first author from teh same year. Name these 2010a, 2010b etc
# dups <- with(short.author.names, table(short, Year)) %>% melt()
# dups <- dups[dups$value > 1, ]
# for(i in 1:nrow(dups)){
#   short.author.names$suffix[
#     short.author.names$short == dups$short[i] &
#       short.author.names$Year == dups$Year[i]] <- letters[1:dups$value[i]]
# }
# 
# # Add the AuthorYear column to the dataframe of effect sizes
# short.author.names <- short.author.names %>%
#   mutate(AuthorYear = paste(short, " ", Year, suffix, sep="")) %>%
#   select(long, AuthorYear)
# prelim.data <- prelim.data %>% 
#   left_join(short.author.names, by = c("Authors" = "long")) 
library(ggthemes)
#Generate a plot
p.meta <- prelim.data %>% 
  mutate(Sex = replace(as.character(Sex), Sex == "B", "Both"),
         Sex = replace(Sex, Sex == "M", "Male"),
         Sex = replace(Sex, Sex == "F", "Female")) %>%

  ggplot(aes(y=reorder(AuthorYear, -g), x = g)) +

  scale_color_brewer(name = "Relationship\nto fitness", 
                    palette = "Set1", 
                    breaks=c("Ambiguous","Indirect","Direct"))+

  scale_shape_manual(values=c(21,22,24))+

  scale_fill_brewer(name = "Relationship\nto fitness", 
                    palette = "Set1", 
                    breaks=c("Ambiguous","Indirect","Direct"))+

  geom_errorbarh(aes(xmin = lowerci, 
                     xmax = upperci,
                     color = Outcome.Class), height = 0.1, show.legend = FALSE) +

  geom_point(aes(shape = Sex,
                 fill = Outcome.Class), 
             size = 1.75, 
             color = "grey20") +

  scale_x_continuous(limits=c(-3.35, 12), 
                     breaks = c(-3, -2, -1, 0, 1, 2, 3), 
                     name='                              Standardized Mean Difference (g) \n[positive values indicate sexual selection improves fitness components]') +

  ylab('Reference') +

  geom_vline(xintercept=0, 
             color='black', 
             linetype='dashed')+

  facet_grid(Outcome_f~.,
             labeller = label_wrap_gen(width=23),
             scales= 'free', 
             space='free')+

  guides(fill = guide_legend(override.aes = list(shape = 21, colour = "grey20")))+

  # scale_color_discrete(breaks=c("Ambiguous","Indirect","Direct"))+
  theme_bw()+

  theme(strip.text.y = element_text(angle = 0, size = 8, margin = margin(t=15, r=15, b=15, l=15)), 
        strip.background = element_rect(colour = NULL,
                                        linetype = "blank",
                                        fill = "gray90"),
        text = element_text(size=11),
        panel.spacing = unit(0.5, "lines"),
        panel.border= element_blank(),
        axis.line=element_line(), 
        panel.grid.major.x = element_line(linetype = "solid", colour = "gray95"),
        panel.grid.major.y = element_line(linetype = "solid", color = "gray95"),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(), 
        legend.text = element_text(size=12), 
        legend.title=element_text(size=12, 
                                  face = "bold"),
        axis.title.x = element_text(hjust = 0, size = 12))

ggsave(plot = p.meta, filename = "figures/Big_forest_plot.eps", height = 18, width = 12)
p.meta

# svg("figures/Big_forest_plot.svg", width=12, height=18)
# p.meta
# dev.off()
```
<br></br>
**Figure S1:** Forest plot of raw effect sizes and their 95% confidence intervals, grouped according to environment (stressed or unstressed) and the sex of the individuals whose fitness trait was measured (male, female, or both sexes mixed together). Rows with multiple data points denote studies that provided multiple effect sizes. Positive values indicate fitness benefits of sexual selection.

<!-- ###Quantitative summary using bootstrapped means -->

<!-- We can obtain a bootstrap weighted mean for the entire dataset. Although this does not take into account any moderator variables it does provide a rough guide on where most of the datapoints sit:  -->

<!-- ```{r} -->
<!-- #Run function -->
<!-- get.CIs.for.weighted.mean <- function(x, weights){ -->
<!--   total.resamples <- 10000 -->
<!--   num.chunks <- ceiling(length(x)*total.resamples / 10^7) # To be nice to RAM, let's keep these to ten million or less  -->
<!--   if(num.chunks == 1){ -->
<!--     rand <- sample(length(x), length(x)*total.resamples, replace = TRUE) -->
<!--     resampled.weighted.means <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:total.resamples, each = length(x))) %>%  -->
<!--       group_by(replicate) %>%  -->
<!--       summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean -->
<!--   } -->

<!--   else{ -->
<!--     resampled.weighted.means <- vector(mode = "list", length = 0) -->
<!--     number.of.resamples <- floor(total.resamples/num.chunks) -->
<!--     final.chunk.size <- total.resamples - number.of.resamples * (num.chunks-1) -->
<!--     for(i in 1:num.chunks){ -->
<!--       if(i == num.chunks) number.of.resamples <- final.chunk.size -->
<!--       rand <- sample(length(x), length(x) * number.of.resamples, replace = TRUE) -->
<!--       resampled.weighted.means[[i]] <- data.frame(x = x[rand], w = weights[rand], replicate = rep(1:number.of.resamples, each = length(x))) %>%  -->
<!--         group_by(replicate) %>%  -->
<!--         summarise(w.mean = weighted.mean(x, w)) %>% .$w.mean -->
<!--     } -->
<!--     resampled.weighted.means <- unlist(resampled.weighted.means) -->
<!--   } -->

<!--   data.frame(w.mean = median(resampled.weighted.means), -->
<!--              lowerCI = quantile(resampled.weighted.means, probs = 0.025) %>% as.numeric(), -->
<!--              upperCI = quantile(resampled.weighted.means, probs = 0.975) %>% as.numeric()) -->
<!-- } -->

<!-- #Get weights -->
<!-- prelim.data$Standard.weights <- (1/prelim.data$var.g) -->

<!-- #Run function with weights -->
<!-- get.CIs.for.weighted.mean(prelim.data$g, prelim.data$Standard.weights) %>% pander() -->
<!-- ``` -->

###Meta-analysis of individual outcomes

We can run individual standard random effects models for each outcome. From the intercept only model we can obtain a mean (beta) and confidence intervals. Following that we can obtain estimates for _I^2^_, the % of residual heterogeneity for each given outcome.

**Table S6** Summary of individual model results, including _I^2^_, for all outcomes with n>3 (fix this).

```{r, warning = FALSE}
outcome.list <- as.list(c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success'))
names(outcome.list) <- c('Behavioural Plasticity', 'Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
outcome.models <-  llply(outcome.list, function(x) rma.mv(g, var.g, 
                          mods = ~ 1, 
                          method = "REML",
                          random = ~ 1 + Study.ID,
                          subset = (Outcome_f == x),
                          data = prelim.data))

df.list <- as.data.frame(do.call("rbind", outcome.models)) # data frame of model results

simple.frame <- subset(df.list, select=c("b", "zval", "ci.lb", "ci.ub", "k", "pval"))
# simple.frame$vi <- as.matrix(simple.frame$vi)
# simple.frame$W <- diag(1/(simple.frame$vi))
# 
# XO <- model.matrix(model.complete2)
# PO <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
# 100 * sum(model.complete2$sigma2) / (sum(model.complete2$sigma2) + (model.complete2$k-model.complete2$p)/sum(diag(P)))

#I couldn't get mapply to work when calculating I2 so I calculated them manually.

#Body Size 
restricted.dataBS <- prelim.data %>% filter(prelim.data$Outcome == "Body Size")

#Run estimate of heterogeneity
WBS = diag(1/restricted.dataBS$var.g)
XBS = model.matrix(outcome.models[["Body Size"]])
PBS = WBS - WBS %*% XBS %*% solve(t(XBS) %*% WBS %*% XBS) %*% t(XBS) %*% WBS
BodySizeI2 <- 100 * sum(outcome.models[["Body Size"]]$sigma2) / (sum(outcome.models[["Body Size"]]$sigma2) + (outcome.models[["Body Size"]]$k-outcome.models[["Body Size"]]$p)/sum(diag(PBS)))

#Development Rate 
restricted.dataDR <- prelim.data %>% filter(prelim.data$Outcome == "Development Rate")

#Run estimate of heterogeneity
W = diag(1/restricted.dataDR$var.g)
X = model.matrix(outcome.models[["Development Rate"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
DevelopmentRateI2 <- 100 * sum(outcome.models[["Development Rate"]]$sigma2) / (sum(outcome.models[["Development Rate"]]$sigma2) + (outcome.models[["Development Rate"]]$k-outcome.models[["Development Rate"]]$p)/sum(diag(P)))

#Early Fecundity 
restricted.dataEF <- prelim.data %>% filter(prelim.data$Outcome == "Early Fecundity")

#Run estimate of heterogeneity
W = diag(1/restricted.dataEF$var.g)
X = model.matrix(outcome.models[["Early Fecundity"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
EarlyFecundityI2 <- 100 * sum(outcome.models[["Early Fecundity"]]$sigma2) / (sum(outcome.models[["Early Fecundity"]]$sigma2) + (outcome.models[["Early Fecundity"]]$k-outcome.models[["Early Fecundity"]]$p)/sum(diag(P)))

#Immunity
restricted.dataI <- prelim.data %>% filter(prelim.data$Outcome == "Immunity")

#Run estimate of heterogeneity
W = diag(1/restricted.dataI$var.g)
X = model.matrix(outcome.models[["Immunity"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
ImmunityI2 <- 100 * sum(outcome.models[["Immunity"]]$sigma2) / (sum(outcome.models[["Immunity"]]$sigma2) + (outcome.models[["Immunity"]]$k-outcome.models[["Immunity"]]$p)/sum(diag(P)))

#Mating Duration
restricted.dataMD <- prelim.data %>% filter(prelim.data$Outcome == "Mating Duration")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMD$var.g)
X = model.matrix(outcome.models[["Mating Duration"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingDurationI2 <- 100 * sum(outcome.models[["Mating Duration"]]$sigma2) / (sum(outcome.models[["Mating Duration"]]$sigma2) + (outcome.models[["Mating Duration"]]$k-outcome.models[["Mating Duration"]]$p)/sum(diag(P)))

#Mutant Frequency
restricted.dataMF <- prelim.data %>% filter(prelim.data$Outcome == "Mutant Frequency")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMF$var.g)
X = model.matrix(outcome.models[["Mutant Frequency"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MutantFrequencyI2 <- 100 * sum(outcome.models[["Mutant Frequency"]]$sigma2) / (sum(outcome.models[["Mutant Frequency"]]$sigma2) + (outcome.models[["Mutant Frequency"]]$k-outcome.models[["Mutant Frequency"]]$p)/sum(diag(P)))

#Fitness Senescence
restricted.dataFS <- prelim.data %>% filter(prelim.data$Outcome == "Fitness Senescence")

#Run estimate of heterogeneity
W = diag(1/restricted.dataFS$var.g)
X = model.matrix(outcome.models[["Fitness Senescence"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
FitnessSenescenceI2 <- 100 * sum(outcome.models[["Fitness Senescence"]]$sigma2) / (sum(outcome.models[["Fitness Senescence"]]$sigma2) + (outcome.models[["Fitness Senescence"]]$k-outcome.models[["Fitness Senescence"]]$p)/sum(diag(P)))

#Lifespan
restricted.dataL <- prelim.data %>% filter(prelim.data$Outcome == "Lifespan")

#Run estimate of heterogeneity
W = diag(1/restricted.dataL$var.g)
X = model.matrix(outcome.models[["Lifespan"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
LifespanI2 <- 100 * sum(outcome.models[["Lifespan"]]$sigma2) / (sum(outcome.models[["Lifespan"]]$sigma2) + (outcome.models[["Lifespan"]]$k-outcome.models[["Lifespan"]]$p)/sum(diag(P)))

#Male Attractiveness
restricted.dataMA <- prelim.data %>% filter(prelim.data$Outcome == "Male Attractiveness")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMA$var.g)
X = model.matrix(outcome.models[["Male Attractiveness"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MaleAttractivenessI2 <- 100 * sum(outcome.models[["Male Attractiveness"]]$sigma2) / (sum(outcome.models[["Male Attractiveness"]]$sigma2) + (outcome.models[["Male Attractiveness"]]$k-outcome.models[["Male Attractiveness"]]$p)/sum(diag(P)))

#Mating Frequency
restricted.dataMF <- prelim.data %>% filter(prelim.data$Outcome == "Mating Frequency")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMF$var.g)
X = model.matrix(outcome.models[["Mating Frequency"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingFrequencyI2 <- 100 * sum(outcome.models[["Mating Frequency"]]$sigma2) / (sum(outcome.models[["Mating Frequency"]]$sigma2) + (outcome.models[["Mating Frequency"]]$k-outcome.models[["Mating Frequency"]]$p)/sum(diag(P)))

#Mating Latency
restricted.dataML <- prelim.data %>% filter(prelim.data$Outcome == "Mating Latency")

#Run estimate of heterogeneity
W = diag(1/restricted.dataML$var.g)
X = model.matrix(outcome.models[["Mating Latency"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingLatencyI2 <- 100 * sum(outcome.models[["Mating Latency"]]$sigma2) / (sum(outcome.models[["Mating Latency"]]$sigma2) + (outcome.models[["Mating Latency"]]$k-outcome.models[["Mating Latency"]]$p)/sum(diag(P)))

#Mating Success
restricted.dataMS <- prelim.data %>% filter(prelim.data$Outcome == "Mating Success")

#Run estimate of heterogeneity
W = diag(1/restricted.dataMS$var.g)
X = model.matrix(outcome.models[["Mating Success"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
MatingSuccessI2 <- 100 * sum(outcome.models[["Mating Success"]]$sigma2) / (sum(outcome.models[["Mating Success"]]$sigma2) + (outcome.models[["Mating Success"]]$k-outcome.models[["Mating Success"]]$p)/sum(diag(P)))

#Ejaculate Quality and Production
restricted.dataEQ <- prelim.data %>% filter(prelim.data$Outcome == "Ejaculate Quality and Production")

#Run estimate of heterogeneity
W = diag(1/restricted.dataEQ$var.g)
X = model.matrix(outcome.models[["Ejaculate Quality and Production"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
EjaculateQualityI2 <- 100 * sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) / (sum(outcome.models[["Ejaculate Quality and Production"]]$sigma2) + (outcome.models[["Ejaculate Quality and Production"]]$k-outcome.models[["Ejaculate Quality and Production"]]$p)/sum(diag(P)))

#Extinction Rate
restricted.dataER <- prelim.data %>% filter(prelim.data$Outcome == "Extinction Rate")

#Run estimate of heterogeneity
W = diag(1/restricted.dataER$var.g)
X = model.matrix(outcome.models[["Extinction Rate"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
ExtinctionRateI2 <- 100 * sum(outcome.models[["Extinction Rate"]]$sigma2) / (sum(outcome.models[["Extinction Rate"]]$sigma2) + (outcome.models[["Extinction Rate"]]$k-outcome.models[["Extinction Rate"]]$p)/sum(diag(P)))

#Offspring Viability
restricted.dataOV <- prelim.data %>% filter(prelim.data$Outcome == "Offspring Viability")

#Run estimate of heterogeneity
W = diag(1/restricted.dataOV$var.g)
X = model.matrix(outcome.models[["Offspring Viability"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
OffspringViabilityI2 <- 100 * sum(outcome.models[["Offspring Viability"]]$sigma2) / (sum(outcome.models[["Offspring Viability"]]$sigma2) + (outcome.models[["Offspring Viability"]]$k-outcome.models[["Offspring Viability"]]$p)/sum(diag(P)))

#Reproductive Success
restricted.dataRS <- prelim.data %>% filter(prelim.data$Outcome == "Reproductive Success")

#Run estimate of heterogeneity
W = diag(1/restricted.dataRS$var.g)
X = model.matrix(outcome.models[["Reproductive Success"]])
P = W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
ReproductiveSuccessI2 <- 100 * sum(outcome.models[["Reproductive Success"]]$sigma2) / (sum(outcome.models[["Reproductive Success"]]$sigma2) + (outcome.models[["Reproductive Success"]]$k-outcome.models[["Reproductive Success"]]$p)/sum(diag(P)))

simple.frame$I2 <- c(NA, BodySizeI2, DevelopmentRateI2, EarlyFecundityI2, ImmunityI2, MatingDurationI2, NA, MutantFrequencyI2, FitnessSenescenceI2, LifespanI2, MaleAttractivenessI2, MatingFrequencyI2, MatingLatencyI2, MatingSuccessI2, NA, EjaculateQualityI2, ExtinctionRateI2, OffspringViabilityI2, ReproductiveSuccessI2)

outcome.frame <- format(simple.frame, digits = 2)
outcome.frame <- add_rownames(outcome.frame, "Outcome")
outcome.frame$b <- as.numeric(outcome.frame$b)
outcome.frame$k <- as.numeric(outcome.frame$k)
outcome.frame$ci.lb <- as.numeric(outcome.frame$ci.lb)
outcome.frame$ci.ub <- as.numeric(outcome.frame$ci.ub)
outcome.frame$I2 <- as.numeric(outcome.frame$I2)

outcome.frame %>% pander(split.cell = 40, split.table = Inf)

#Can't get the llply or mapply to work on the list of outcomes

# I2df <- llply(outcome.models, function(x) {
#   prelim.data %>% filter(prelim.data$Outcome == outcome.list)
# })
#   #Run estimate of heterogeneity
# Wlist <- llply(outcome.list, function(x) {diag(1/I2df[[x]]$var.g)}) #X
# 
# Xlist <- llply(outcome.list, function(x) {model.matrix(outcome.models[[x]])}) #Y
# 
# Pfunc <- Map(function(X,Y,Z) {
#   X[[Z]] - X[[Z]] %*% Y[[Z]] %*% solve(t(Y[[Z]]) %*% X[[Z]] %*% Y[[Z]]) %*% t(Y[[Z]]) %*% X[[Z]]},
#   X=Wlist, Y=Xlist, Z=1:19)
# 
# llply()
# 
# I2list <- llply(outcome.list, function(x) {100 * sum(outcome.models[[x]]$sigma2) / (sum(outcome.models[[x]]$sigma2) + (outcome.models[[x]]$k-outcome.models[[x]]$p)/sum(diag(Wlist - Wlist %*% Xlist %*% solve(t(Xlist) %*% Wlist %*% Xlist) %*% t(Xlist) %*% x)))})
# 
# matrix(outcome.list)
```

<!-- Check the results on a plot -->
<!-- ```{r} -->
<!-- pd <- position_dodgev(height = .7) -->
<!-- outcome.frame %>% ggplot(aes(x = b, y= Outcome)) +  -->
<!--   geom_vline(xintercept = 0, linetype = 2, colour = "grey70") +  -->
<!--   geom_errorbarh(aes(xmin = ci.lb,  -->
<!--                      xmax = ci.ub), height = 0, position = pd, show.legend = F) + -->
<!--   geom_point(position = pd, color = "grey20") +  -->
<!--   ylab("Outcome\n")+ -->
<!--   xlab("\nEffect Size (Hedges g)")+ -->
<!--   xlim(-2.5, 2.5)+ -->
<!--   ggtitle('Standard Random Effects Model') -->
<!-- ``` -->

@@

@@

<input type=button class=hideshow></input>
```{r}
model.preliminary <- rma.mv(g, var.g, 
                         mods = ~ 1 + Sex * Environment + Taxon + Outcome.Class + Generations + Blinding, # << ----- Add big model, then cull predictors to this one
                         random = list(~ 1 | Study.ID, 
                                       ~ 1 | Outcome), 
                         method = "REML", 
                         data = prelim.data)

summary(model.preliminary)
```
<br></br>

@@

<input type=button class=hideshow></input>
```{r, warning=FALSE}
#Restrict the dataset for unambiguous outcomes and environments 
restricted.data <- prelim.data %>% 
  filter(Outcome.Class != "Ambiguous" & Environment != "Not Stated") %>% 
  mutate(Sex = as.character(Sex), 
         Environment = as.character(Environment), 
         Outcome.Class.2 = as.character(Outcome.Class), 
         Enforced.Monogamy = as.character(Enforced.Monogamy))

@@

The result is a model with estimates for various taxa, species, sexes and environments. To make sense of these estimates we should obtain average predictions for each moderator variable class of interest. We can do that by using a modified version version of a function used by Holman 2017. Here it alows us to cluster predictions for the different moderators of interest: Sex, environment, taxon etc. This is done by obtaining predictions using the base ``predict()`` function for the ``rma.mv()`` objects that have been previously created
```{r, warning=FALSE}
# function that makes predict.rma work like a normal predict() function, instead of the idiosyncratic way that it works by default.
get.predictions.complete <- function(newdata){
  B<-0; F<-0; Stressed<-0; Cricket<-0; Fly<-0; Guppy<-0; Mite<-0; Mouse<-0; interaction1<-0; interaction2<-0; interaction3<-0
  if(newdata[1] == "B") B<-1 
  if(newdata[1] == "F") F<-1 
  if(newdata[2] == "Stressed") Stressed<-1
  if(newdata[3] == "Cricket") Cricket<-1
  if(newdata[3] == "Fly") Fly<-1
  if(newdata[3] == "Guppy") Guppy<-1
  if(newdata[3] == "Mite") Mite<-1
  if(newdata[3] == "Mouse") Mouse<-1
  if(newdata[1] == "B" & newdata[2] == "Stressed") interaction1<-1
  if(newdata[1] == "F" & newdata[2] == "Stressed") interaction2<-1
